\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[polish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.7in]{geometry}
% \usepackage[margin=1.25in]{geometry}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{blindtext}
\usepackage{tcolorbox}
\usepackage{polski}
\usepackage{multicol}
\usepackage{transparent}
\usepackage{ragged2e}
\usepackage{geometry}

\geometry{
  bottom=3cm
%   footskip=2cm
}



\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{\transparent{0.4} \justify{Wyrażam zgodę na przetwarzanie moich danych osobowych dla potrzeb niezbędnych do realizacji procesu rekrutacji (zgodnie z Ustawą z dnia 29.08.1997 roku o Ochronie Danych Osobowych; tekst jednolity: Dz. U. 2016 r. poz. 922).}}
% \chead{}


\titleformat{\section}
{\huge}
{}
{0em}
{\bfseries}[\titlerule\vspace{-.2cm}]

\titleformat{\subsection}
{\vspace{1em}\bfseries\large}
% {\hspace{-.25in}$\bullet$}
{}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[\hspace{1em}---]

\titlespacing{\subsubsection}
{0em}{.25em}{1em}

\renewcommand{\maketitle}{
    \begin{center}
        % {\Huge\bfseries\thetitle}

        % \vspace{1.5em}


        {\huge\bfseries\theauthor}

        \vspace{.25em}

        +48 888 829 696\\czajka.adam147@gmail.com\\github.com/czajrow
	\end{center}
	\vspace{-.5cm}
}


\begin{document}


\title{CV}
\author{Adam Czajka}

\maketitle

\vspace{2em}

\begin{minipage}[t]{.5\textwidth}
	\section{education}

    \subsection{Warsaw University of Technology}
	\texttt{02/2021 - present}
	\par Applied Computer Science, Faculty of Electrical Engineering, masters degree.

    \subsection{John von Neumann University, Hungary}
	\texttt{9/2019 - 5/2020}
	\par Computer Science, \texttt{Erasmus+} , international studies.

	\subsection{Warsaw University of Technology}
	\texttt{10/2017 - 02/2021}
	\par Applied Computer Science, Faculty of Electrical Engineering, bachelor degree.

	\vspace{2em}

	\section{employment history}

    \subsection{Airnauts}
	\texttt{06/2020 - present}
	\par I am a front-end developer at \texttt{Airnauts} working in projects for international clients.


	\subsection{Erasmus Student Network}
	\texttt{11/2017 - 04/2021}
	\par As part of my work at \texttt{ESN}, I was involved in the organization of events for international students in Warsaw. For two years I was the \texttt{ESN} sports coordinator.

	\subsection{Mały Inżynier}
	\texttt{6/2018 - 2/2019}
	\par\texttt{Mały Inżynier} is a company where I conducted educational classes in programming, experiments, robotics and DIY for children.

	\subsection{Europejska Szkoła Korepetycji}
	\texttt{10/2017 - 6/2019}
	\par W \texttt{Europejskiej Szkole Korepetycji} I conducted individual mathematics and physics lessons for high school students preparing for the matriculation examination.

\end{minipage}\hfill
\begin{minipage}[t]{.4\textwidth}

	\section{completed projects}
	\subsection{Android Studio}
    An application based on Android (Java) technology, in which the \texttt{MLP} neural network (also implemented in Java on my own) conducts the game with the user in the game \texttt{Tic-tac-toe}.
	% Aplikacja w technologii Android (Java), w której sieć neuronowa typu \verb+MLP+ (również zaimplementowana własnoręcznie w języku \verb+Java+) prowadzi rozgrywkę z użytkownikiem w grę \verb+Kółko i Krzyżyk+.

	\subsection{JavaFX}
	\texttt application that uses the \texttt{OpenCV} library to recognize vehicles in the film.

	\subsection{JavaScript}
    Visualization of the \texttt{Monte Carlo} method for computing the definite integral of any mathematical function with a real domain. The \texttt{p5.js} library was used.
	% Wizualizacja metody \verb+Monte Carlo+ do obliczania całki oznaczonej dowolnej funkcji matematycznej o rzeczywistej dziedzinie. Wykorzystana została biblioteka \verb+p5.js+.

	\vspace{1em}

	\section{skills}
    \vspace{1em}
	Angular 2+, TypeScript, JavaScript, HTML, CSS, Java 8, C, MatLab, Python 3, bash/zsh, git, vim, \LaTeX, SQL.

	\subsection{Others}
	basic knowledge of UML, knowledge of basic design patterns, OOP principles, SCRUM methodology.

	\subsection{Languages}
	\subsubsection{English} C1 (IT vocabulary)
    \subsubsection{Polish} Native

	\vspace{1em}

	\section{interests}
    water sports - Polish Rowing Championship medalist, former member of the national rowing team, sea sailor.
	% sporty wodne - multimedalista mistrzostw polski w wioślarstwie, były członek kadry narodowej w wioślarstwie, żeglarz morski.

\end{minipage}

\end{document}
